---
title: "Practical Machine Learning - Week 4 Project"
author: "Bensafouan Abdelhalim"
date: "28/08/2020"
output: html_document
---



```{r setup, include=FALSE}
```

## EXECUTIVE DATA

the purpose of this project is to predict the manner in which poeple do like exercise  , the data was collected by HAR (Human Activity Recognition) , more information is availavle here : http://web.archive.org/web/20161224072740/http:/groupware.les.inf.puc-rio.br/har 

```{r cars}
library(caret)
library(knitr)
library(randomForest)
library(rpart)
library(rpart.plot)
```


## EXPLORATORY DATA ANALYSIS


```{r pressure }
training <- read.csv("pml-training.csv")
testing <- read.csv("pml-testing.csv")

```



 Delete variables that are not related
```{r  }
training <- training[, -c(1:7)]
testing <- testing[, -c(1:7)]
training$classe <- as.factor(training$classe)
# to see wish variables haven't any variability to remove them
training <- training[,-nearZeroVar(training)]

```

```{r  }
inTrain <- createDataPartition(y=training$classe, p=0.75, list=FALSE)
training1 <- training[inTrain,]
testing1 <- training[-inTrain,]
```

we wille use PCA method to reduce the data 

```{r  }
pre <- preProcess(training1[,-length(training1)],method="pca")
dataPCA <- predict(pre,training1[,-length(training1)])
```

## Prediction 

we will use dataPCA as Dataset and random forest as a prediction model and we will test the model by testing Dataset

```{r  }
randomForestModel <- randomForest(classe ~. ,data=training1,na.action = na.roughfix)
randomForestPrediction <- predict(randomForestModel, testing1, type = "class")
confusionMatrix(randomForestPrediction, testing1$classe)
```


Based on the data available, we're able to fit  model with a high degree of accuracy in predicting out of sample observations.
